Automated Topic Naming

### 2011-09-06 ese/ese.tex
figure size

\begin{figure}
  \centering
 \includegraphics[width=.45\textwidth]{figures/process-model}
 \caption{Research methodology process view.}
  \label{fig:process}
\end{figure}

@@

\begin{figure*}[t]
  \centering
 \includegraphics[width=0.8\textwidth]{figures/unsupervised-bar}
 \caption{Performance, ROC values (range: $0$--$1$), of semi-unsupervised topic labelling for
   each NFR and per word-list. The dashed line indicates the performance of a random classifier. This graph shows how well the
   semi-unsupervised topic labelling matched our manual annotations.}

@@

% PG data from abram's email of 09/01/2011 using first column and pgsqln.
\begin{figure}[t]
\centering
\includegraphics[width=0.45\textwidth]{figures/both-supervised}
\caption[]{ROC value for the best learner per label for MaxDB, MySQL and PgSQL. Values range from $0$--$1$.  Dashed line indicates the performance of a random
classifier.
}
\label{fig:best-learn-per-tag}
\end{figure}

@@

\subsection{Annotation Observations}
We found many topics that were not actually non-functional requirements (NFRs) but were often related to them. 
For instance, concurrency was mentioned often in the commit logs and
was related to \emph{correctness} and \emph{reliability}, possibly because concurrent code is prone to bugs such as race conditions. %are 
% often  was troublesome. 
\emph{Configuration management} and \emph{source control} related changes appeared often; % and sometimes there were topics dedicated to configuration
management. 
these kinds of changes are slightly related to \emph{maintainability}. 
A non-functional change that was not quality-related was licensing and
copyright; many changes were simply to do with updating copyrights or
ensuring copyright or license headers were applied to files. In these
cases we assigned the \emph{None} label to the topic.

@@

Table \ref{tab:interr} describes the Cohen Kappa and the Spearman
correlation of our per topic annotations for each tag. We had to
evaluate inter-rater reliability this way because 1 topic could be
tagged with more than 1 annotation.

>>>>

\begin{figure}
  \centering
 \includegraphics[height=.6\textheight]{figures/process-model}
 \caption{Research methodology process view.}
  \label{fig:process}
\end{figure}

@@

\begin{figure*}[t]
  \centering
 \includegraphics[width=0.9\textwidth]{figures/unsupervised-bar}
 \caption{Performance, ROC values (range: $0$--$1$), of semi-unsupervised topic labelling for
   each NFR and per word-list. The dashed line indicates the performance of a random classifier. This graph shows how well the
   semi-unsupervised topic labelling matched our manual annotations.}

@@

% PG data from abram's email of 09/01/2011 using first column and pgsqln.
\begin{figure}[t]
\centering
\includegraphics[width=0.7\textwidth]{figures/both-supervised}
\caption[]{ROC value for the best learner per label for MaxDB, MySQL and PgSQL. Values range from $0$--$1$.  Dashed line indicates the performance of a random
classifier.
}
\label{fig:best-learn-per-tag}
\end{figure}

@@

\subsection{Annotation Observations}
We found many topics that were not actually non-functional requirements (NFRs) but were often related to them. 
For instance, concurrency was mentioned often in the commit logs and
was related to \emph{correctness} and \emph{reliability}, possibly because concurrent code is prone to bugs such as race conditions. %are 
% often  was troublesome. 
\emph{Configuration management} and \emph{source control} related changes appeared often; % and sometimes there were topics dedicated to configuration
% management. 
these kinds of changes are slightly related to \emph{maintainability}. 
A non-functional change that was not quality-related was licensing and
copyright; many changes were simply to do with updating copyrights or
ensuring copyright or license headers were applied to files. In these
cases we assigned the \emph{None} label to the topic.

@@

Table \ref{tab:interr} describes the Cohen Kappa and the Spearman
correlation of our per topic annotations for each NFR. We had to
evaluate inter-rater reliability this way because 1 topic could be
tagged with more than 1 NFR.
